---
title: "This had better work or imma start crying fam hee haww"
subtitle: "No cap imma start crying homes"
author: 
  - Mohammad Sardar Sheikh
thanks: "Code and data are available at: https://github.com/mohammadsardar/mojo "
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(dplyr)
library(lubridate)
library(knitr)
library(opendatatoronto)
library(haven)


```

# Introduction

This paper was made using @citeR
 



# Data

Our data is of homeless shelters in Toronto

```{r, include=FALSE}
#loading in the data
cleaned_toronto_shelters <- read_csv("cleaned_toronto_shelters.csv")

```

```{r, echo=FALSE}
#creating a new month variable
toronto_shelters_clean <- cleaned_toronto_shelters %>% 
  mutate(occupancy_month = month(occupancy_date, 
                                 label = TRUE, 
                                 abbr = FALSE))

#toronto_shelters_clean <- toronto_shelters_clean %>% 

#there is only one province so this wont work
#toronto_shelters_clean <- toronto_shelters_clean %>% 
#  mutate(cold_extremelycold = ifelse(location_province == "ON" | location_province =="QC" | location_province =="BC", "cold", "extremely cold"))

#toronto_shelters_clean %>% 
 # group_by(occupancy_month)%>%
  #summarise(n = mean(occupied_beds)) %>% 
  #kable()

toronto_shelters_clean %>% group_by(occupancy_month)%>%
  summarise(n = mean(occupied_beds)) %>% 
  ggplot(mapping = aes(n, occupancy_month)) +
  geom_boxplot() +
  theme_minimal() + # Make the theme neater
  coord_flip() + # Swap the x and y axis to make parties easier to read
  labs(x = "average number of beds occupied",
       y = "Month",
       caption =  "Monthly Average number of homeless shelter beds occupied")

```


Talk more about it.





```{r, echo=FALSE}

toronto_shelters_clean %>% 
  group_by(occupancy_month)%>%
  summarise(n = mean(capacity_actual_bed)) %>% 
  kable(caption = "Average number of Available Beds in Homeless shelters in 2021", 
        col.names = c("Month", "Average number of available beds"),
        digits = 1,
        booktabs = TRUE,
        linesep = ""
  )
```


Talk way more about it. 




# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


